Case Study: scRNA-seq (Human data, scDD method)

### 2018-03-14 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Change human dataset comparison
Previous comparison used very different cell types, resulting in almost everything
being significant. Here we compare the neoplastic cells found in glioblastoma
tumors versus the surrounding tissue (periphery).

This dataset (from PMC5810554) contains cells from four Glioblastoma patients, 
sampled from both the tumor core as well as the tissue peripheral to the tumor. 
We'll compare the Immune cells in the tumor vs periphery.

@@

  # subset by groups of interest
  humandata <- humandata[, (colData(humandata)$tissue.ch1 %in% 
                         c(" Tumor", " Periphery")) &
                         colData(humandata)$cell.type.ch1 == " Immune cell" ]
  cdata=colData(humandata)
  cdata$group <- cdata$tissue.ch1

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="meanExp", maxy=35,
           main = "MAST, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="detection", maxy=35,
           main = "MAST, Covariate 2: Detection Rate") 
```

>>>>

This dataset (from PMC5810554) contains cells from four Glioblastoma patients, 
sampled from both the tumor core as well as the tissue peripheral to the tumor. 
We'll compare the Neoplastic cells in the tumor core vs periphery. We'll exclude 
the two samples where only a few neoplastic cells were found in the periphery.

@@

  # subset by groups of interest
  humandata <- humandata[, colData(humandata)$patient.id.ch1 %in% 
                           c(" BT_S4", " BT_S2") &
                           colData(humandata)$cell.type.ch1 == " Neoplastic" ]
  cdata=colData(humandata)
  cdata$group <- cdata$tissue.ch1

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="meanExp", maxy=12,
           main = "MAST, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="mast_p", covariate="detection", maxy=12,
           main = "MAST, Covariate 2: Detection Rate") 
```

### 2018-03-14 datasets/scrnaseq/scrnaseq-human-scdd.Rmd
Change human dataset comparison
Previous comparison used very different cell types, resulting in almost everything
being significant. Here we compare the neoplastic cells found in glioblastoma
tumors versus the surrounding tissue (periphery).

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="meanExp", maxy=35,
           main = "scDD, Covariate 1: Mean Nonzero Expression") 
```

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="detection", maxy=35,
           main = "scDD, Covariate 2: Detection Rate") 
```
## Multiple-Testing Correction

>>>>

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="meanExp", maxy=12,
           main = "scDD, Covariate 1: Mean Nonzero Expression") 
```

@@

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="detection", maxy=12,
           main = "scDD, Covariate 2: Detection Rate") 
```
## Multiple-Testing Correction
